The 2018 heatwave and its implications on ozone induced damage on vegetation in a subarctic climate

### 2020-05-15 VegOzone.tex
Added new plots and citations.

The \chem{\left<\Delta\left<[O_3]\right>\right>} for Svanvik in 2018 is slightly larger than for Esrange and Pallas. This could mean either that 2018 had been more exceptional at Svanvik or the derived climatology may need a correction for increased tropospheric background ozone concentration. Based on the meteorological conditions, we assume 2019 as average year which leads to a constant bias of about $1.2\,\unit{ppb}$. Daily \chem{\Delta_{present-past}\left<[O_3]\right>} from Esrange and Pallas, wherein present is defined as the average of 2010--2018 and past as the respective beginning of data taking until 1997, do not reveal a clear trend: We find for Esrange $(1.5\pm 3.1)\,\unit{ppb}$ and for Pallas $(-2.5\pm 3.7)\,\unit{ppb}$. Former is compatible with our assumed bias for the climatology derived for Svanvik.

>>>>

The \chem{\left<\Delta\left<[O_3]\right>\right>} for Svanvik in 2018 is slightly larger than for Esrange and Pallas. This could mean either that 2018 had been more exceptional at Svanvik or the derived climatology may need a correction for increased tropospheric background ozone concentration. Based on the meteorological conditions, we assume 2019 as average year which leads to a constant bias of about $1.2\,\unit{ppb}$. Daily \chem{\Delta_{present-past}\left<[O_3]\right>} from Esrange and Pallas, wherein present is defined as the average of 2010--2018 and past as the respective beginning of data taking until 1997, do not reveal a clear trend: We find for Esrange $(1.5\pm 3.1)\,\unit{ppb}$ and for Pallas $(-2.5\pm 3.7)\,\unit{ppb}$ \citep{NILU2003, BER:Ruoho-Airola2015}. Former is compatible with our assumed bias for the climatology derived for Svanvik.
